Aa Language Reference Manual

### 2013-09-03 v2/Ahir-asm/devel/docs/AaLRM.tex
Some more bugs, simple processor seems to run (for a while) at 3-cycle latency until dependencies catch up!
Simple processor works ok.  Time to try the extreme pipelining here to figure out if any benefits accrue...

@@

\subsection{Pipelinable-loops: the {\bf do-while} construct}

The \Aa language provides a single construct for describing loops.
The form of the construct is
\begin{verbatim}
  $do
     $merge $entry $loopback
       <phi-statements>
     $endmerge
     atomic-statement-sequence
  $while <condition-expression>
\end{verbatim}
The do-while statement can appear only in branch-blocks.  Control enters
the do-while from a predecessor in the branch-block, and stays in the
do-while as long as the condition-expression is false.  The \$loopback
place is used to repeat the loop-body.  The leading merge statement
in the do-while is used to merge the control-flow coming in either from
the entry to the do-while or from the loopback place.

The downstream tools will always attempt to pipeline the do-while loop by
starting the next iteration while the current one is still in progress.
Dependency analysis on values in the loop-body is used to determine the
extent of loop pipelining.  Note that it is always possible to describe
a do-while loop using a branch-block, and this is what should be done
if loop-pipelining is not desired.

>>>>

Complete atomic statements can have a guard predicate
specified, so that they are executed only if the guard
predicate is true.  This is specified either by
\begin{verbatim}
$guard ( <guard-variable> )  <statement-spec>
\end{verbatim}
or 
\begin{verbatim}
$guard ( ~ <guard-variable> )  <statement-spec>
\end{verbatim}
For example
\begin{verbatim}
$guard (sel_add) r := (a + b)
\end{verbatim}
or
\begin{verbatim}
$guard (~ sel_add) $call afun (a b) (r)
\end{verbatim}

@@

\subsection{Pipelinable-loops: the {\bf dopipeline-while} construct}

The \Aa language provides a single construct for describing loops.
The form of the construct is
\begin{verbatim}
  $dopipeline
     $merge $entry $loopback
       <phi-statements>
     $endmerge
     atomic-statement-sequence
  $while <condition-expression>
\end{verbatim}
The do-while statement can appear only in branch-blocks.  Control enters
the do-while from a predecessor in the branch-block, and stays in the
do-while as long as the condition-expression is false.  The \$loopback
place is used to repeat the loop-body.  The leading merge statement
in the do-while is used to merge the control-flow coming in either from
the entry to the do-while or from the loopback place.

The downstream tools will always attempt to pipeline the do-while loop by
starting the next iteration while the current one is still in progress.
Dependency analysis on values in the loop-body is used to determine the
extent of loop pipelining.  While doing the pipelining, one can specify
two parameters as follows
\begin{verbatim}
  $dopipeline $depth 8 $buffering 2
    ...
  $while ....
\end{verbatim}
This specifies that up to 8 iterations of the loops will be kept alive
in hardware, and the amount of buffering per operation will be kept to
2.

Note that it is always possible to describe
a do-while loop using a branch-block, and this is what should be done
if loop-pipelining is not desired.
